Modeling Intervention Strategies for United States TB Control

### 2013-10-14 in_progress/presentations/paper/draft.tex
changed appendix citations

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
Model) were implemented in 
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The systems of differential equations usedto capture basic disease dynamics in the Basic Hill Model and the Extended Hill Model are
shown below in Figure 2 and Figure 3 respectively. In the Extended Hill Model,
more differential equations were implemented to add additional tracking and
economic modeling. These equations are detailed in the Appendix.

@@

The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of
US-born individuals in the S, F, L, I, J compartments respectively, whereas $S_{1},
F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.  $N_{0}$ and
$N_{1}$ are the total populations of US-born and foreign-born individuals.
The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
A complete list and descriptions of all constants used in the model can be found in the appendix.

>>>>

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
Model) were implemented in 
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The systems of differential equations usedto capture basic disease dynamics in the Basic Hill Model and the Extended Hill Model are
shown below in Figure 2 and Figure 3 respectively. In the Extended Hill Model,
more differential equations were implemented to add additional tracking and
economic modeling. These equations are detailed in the Appendix, Section 7.2.

@@

The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of
US-born individuals in the S, F, L, I, J compartments respectively, whereas $S_{1},
F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.  $N_{0}$ and
$N_{1}$ are the total populations of US-born and foreign-born individuals.
The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
A complete list and descriptions of all constants used in the model can be found in the Appendix,
Section 7.1.
